Notes on symmetrizing the FDFD matrix with stretched-coordinate PML.

### 2012-02-06 scribblings/symmA.tex
Minor edit.
Updated symm A.

\documentclass{article}
\usepackage{amsmath}
\usepackage{pstricks}
\newcommand{\BE}{\begin{equation}}
\newcommand{\EE}{\end{equation}}
\newcommand{\D}{\Delta}
\title{Notes on symmetrizing the FDFD matrix with stretched-coordinate PML.}
\author{Jesse Lu, Wonseok Shin}
\begin{document}
\maketitle
We want to find a diagonal matrix 
    \BE D = \text{diag}(d) \EE
    such that
    \BE (AD)^T = AD, \EE
    where $A = \nabla \times \nabla \times$ is the system matrix
    for the finite-difference frequency-domain problem
    for Maxwell's equations.

@@

First we note that,
    \BE (AD)^T = DA^T \EE
    \BE (AD)_{ij} = A_{ij} d_j \EE
    \BE (DA^T)_{ij} = d_i (A^T)_{ij} = A_{ji} d_i, \EE
    and so state our problem as finding $d$ such that
\BE A_{ij} d_j = A_{ji} d_i, \quad \text{for all $i, j$.} \EE

@@

To do so, we observe that from figure~\ref{fig1} we can deduce that the
    $\nabla \times \nabla \times$ operation will result in
    \BE A_{ba} = -\frac{1}{\D x_b \D y_b} \EE
    \BE A_{ab} = -\frac{1}{\D x_a \D y_a}, \EE
    from which we conclude that
    \BE d_i \propto \frac{1}{\D x_i \D y_i}. \EE

Similarly, if we replace $b \to c$ and $\D y_{a,b} \to \D z_{a,c}$ 
    in the figure, then we have
    \BE A_{ca} = -\frac{1}{\D x_b \D z_b} \EE
    \BE A_{ac} = -\frac{1}{\D x_a \D z_a}, \EE
    which leads to
    \BE d_i \propto \frac{1}{\D x_i \D z_i}. \EE

We then conclude that the choice of 
    \BE d_i = \frac{1}{\D x_i \D y_i \D z_i} \EE
    will lead to symmetric $AD$.
Note that none of the $A_{aa'}$ terms need to be included,
    where $a$ and $a'$ point in the same direction,
    since $A_{aa'} = A_{a'a}$ will hold both with or without the preconditioner.

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{pstricks}
\newcommand{\BE}{\begin{equation}}
\newcommand{\EE}{\end{equation}}
\newcommand{\D}{\Delta}
\title{Notes on symmetrizing the FDFD matrix with stretched-coordinate PML.}
\author{Jesse Lu}
\begin{document}
\maketitle
We want to find a diagonal matrix 
    \BE D = \text{diag}(d) \EE
    such that
    \BE (DA)^T = DA, \EE
    where $A = \nabla \times \nabla \times$ is the system matrix
    for the finite-difference frequency-domain problem
    for Maxwell's equations.

@@

First we note that,
    \BE (DA)^T = A^T D \EE
    \BE (DA)_{ij} = A_{ij} d_i \EE
    \BE (A^T D)_{ij} = (A^T)_{ij} d_j = A_{ji} d_j, \EE
    and so state our problem as finding $d$ such that
\BE A_{ij} d_i = A_{ji} d_j, \quad \text{for all $i, j$.} \EE

@@

To do so, we observe that from figure~\ref{fig1} we can deduce that the
    $\nabla \times \nabla \times$ operation will result in
    \BE A_{ba} = -\frac{1}{\D x_b \D y_b} \EE
    \BE A_{ab} = -\frac{1}{\D x_a \D y_a}, \EE
    from which we conclude that
    \BE d_i \propto \D x_i \D y_i. \EE

Similarly, if we replace $b \to c$ and $\D y_{a,b} \to \D z_{a,c}$ 
    in the figure, then we have
    \BE A_{ca} = -\frac{1}{\D x_b \D z_b} \EE
    \BE A_{ac} = -\frac{1}{\D x_a \D z_a}, \EE
    which leads to
    \BE d_i \propto \D x_i \D z_i. \EE

We then conclude that the choice of 
    \BE d_i = \D x_i \D y_i \D z_i \EE
    will lead to symmetric $DA$.
Note that none of the $A_{aa'}$ terms need to be included,
    where $a$ and $a'$ point in the same direction,
    since $A_{aa'} = A_{a'a}$ will hold both with or without the preconditioner.
